Interference Transform: Estimating the frequency and phase of low resolution samples

### 2020-05-23 Papers/01_interf_transf/Interference Transform.tex
web technologies version implemented

  So it's easy to see for each frame of a given discrete wave $W[i]$, there exists an infinite family of continuous sinusoids that pass exactly through the point defined by $i$ and $W[i]$. In fact, almost any sinusoid of the form $a \cos \left( \phi + 2 \pi f \frac{i}{n} \right)$ can be forced to contain the point $(i, W[i])$, given a suitable choice of $a$, with the exception of the particular case where $W[i] \ne 0$ and $\cos \left( \phi + 2 \pi \mathcal{F} \frac{i}{\textrm{fps}} \right)$. Of interest to this work are those sinusoids, as shown in Figure \ref{fig:OptSinusoids}, that have one of their infinite extrema, either maximum or minimum, coinciding with the abscissa $i$ or, setting $a=W[t]$, coincident with the point $(i, W[i])$.

>>>>

  So it's easy to see that, for each frame of a given discrete wave $W[i]$, there exists an infinite family of continuous sinusoids that pass exactly through the point defined by $i$ and $W[i]$. In fact, almost any sinusoid of the form $a \cos \left( \phi + 2 \pi f \frac{i}{n} \right)$ can be forced to contain the point $(i, W[i])$, given a suitable choice of $a$, with the exception of the particular case where $W[i] \ne 0$ and $\cos \left( \phi + 2 \pi \mathcal{F} \frac{i}{\textrm{fps}} \right)$. Of interest to this work are those sinusoids, as shown in Figure \ref{fig:OptSinusoids}, that have one of their infinite extrema, either maximum or minimum, coinciding with the abscissa $i$ or, setting $a=W[t]$, coincident with the point $(i, W[i])$.
